### 2017-07-19 relatedwork.tex
Adding ICPSR to related work. Ack lines and some ref reorg.

>>>>

The ICPSR data enclave \cite{icpsr} at the University of Michigan is a data enclave that hosts sensitive datasets
for social science research. While the majority of the datasets are public, restricted use datasets such as crime
data are protected behind a data enclave. The physical data enclave is a single protected server that is disconnected
from the internet and is accessible only in person. The virtual enclave is a remote desktop solution that is designed
to prevent copying of data. Systems such as this offer security at the cost of accessibility and ease of use and at
the same time have no solution to the fundamental problem of the analyst simply reading sensitive microdata.
